\subsection{Volume rendering data (Parallel volume rendering module)}

Calypso includes parallel volume rendering (PVR) module for scalar field visualization. The PVR module generates volume rendering data during time integration without writing large size volume data.

To output volume rendering data, increment of the volume rendering needs to be defined at \verb|i_step_sectioning_ctl| in \verb|time_step_ctl| block. Parameters foe each rendering are defined in array block \verb|volume_rendering| in \verb|visual_control|. Each  \verb|volume_rendering| block can be stored in an external file, and the external file can be defined as \verb|file volume_rendering [File_Name]|.

\paragraph{Control data}
The control parameters for PVR is the following:
\\
%
Block \verb|volume_rendering| (Top level for volume rendering)
\\
\label{href_i:volume_rendering}
\begin{itemize}
	\item \hyperref[href_t:updated_sign]
			{\tt updated\_sign    [SIGNAL]}
	\item \hyperref[href_t:pvr_file_prefix]
			{\tt pvr\_file\_prefix    [File\_Prefix]}
	\item \hyperref[href_t:pvr_output_format]
			{\tt pvr\_output\_format    [File\_Format]}
	\item \hyperref[href_t:monitoring_mode]
			{\tt monitoring\_mode       [ON/OFF]}
%
	\item \hyperref[href_t:stereo_imaging]
			{\tt stereo\_imaging          [ON/OFF]}
	\item \hyperref[href_t:anaglyph_switch]
			{\tt anaglyph\_switch         [ON/OFF]}
	\item \hyperref[href_t:quilt_3d_imaging]
			{\tt quilt\_3d\_imaging       [ON/OFF]}
%
	\item \hyperref[href_t:output_field]
			{\tt output\_field            [Field\_Name]}
	\item \hyperref[href_t:output_component]
			{\tt output\_component       [Component\_Name]}
%
    	\item File or Block \verb|view_transform_ctl|
				\label{href_i:view_transform_ctl}
		\begin{itemize}
    			\item Block \verb|image_size_ctl|
						\label{href_i:image_size_ctl}
				\begin{itemize}
					\item \hyperref[href_t:x_pixel_ctl]
							{\tt x\_pixel\_ctl   [\# of PIXELS]}
					\item \hyperref[href_t:y_pixel_ctl]
							{\tt y\_pixel\_ctl   [\# of PIXELS]}
				\end{itemize}
%
			\item Array \hyperref[href_t:modelview_matrix_ctl]
					{\tt modelview\_matrix\_ctl   [X/Y/X/W] [X/Y/Z/W]  [VALUE]}
			\item Array \hyperref[href_t:look_at_point_ctl]
					{\tt look\_at\_point\_ctl   [X/Y/Z]    [VALUE]}
			\item Array \hyperref[href_t:eye_position_ctl]
					{\tt eye\_position\_ctl   [X/Y/Z]     [VALUE]}
			\item Array \hyperref[href_t:up_direction_ctl]
					{\tt up\_direction\_ctl   [X/Y/Z]     [VALUE]}
			\item Array \hyperref[href_t:view_rotation_vec_ctl]
					{\tt view\_rotation\_vec\_ctl   [X/Y/Z]     [VALUE]}
			\item \hyperref[href_t:view_rotation_deg_ctl]
					{\tt view\_rotation\_deg\_ctl     [DEGREE]}
			\item \hyperref[href_t:scale_factor_ctl]
					{\tt scale\_factor\_ctl     [SCALE]}
			\item Array \hyperref[href_t:scale_factor_vec_ctl]
					{\tt scale\_factor\_vec\_ctl  [X/Y/Z]     [SCALE]}
			\item Array \hyperref[href_t:eye_position_in_viewer_ctl]
					{\tt eye\_position\_in\_viewer\_ctl   [X/Y/Z]    [VALUE]}
%
			\item \hyperref[href_t:projection_type_ctl]
					{\tt projection\_type\_ctl   [TYPE]}
%
   			\item Block \verb|projection_matrix_ctl|
						\label{href_i:projection_matrix_ctl}
				\begin{itemize}
					\item \hyperref[href_t:perspective_angle_ctl]
							{\tt perspective\_angle\_ctl   [DEGREE]}
					\item \hyperref[href_t:perspective_xy_ratio_ctl]
							{\tt perspective\_xy\_ratio\_ctl   [ASPECT]}
					\item \hyperref[href_t:perspective_near_ctl]
							{\tt perspective\_near\_ctl   [NEAR\_DISTANCE]}
					\item \hyperref[href_t:perspective_far_ctl]
							{\tt perspective\_far\_ctl   [FAR\_DISTANCE]}
%
%					\item \hyperref[href_t:horizontal_range_ctl]
%							{\tt horizontal\_range\_ctl   [LEFT]  [RIGHT[}
%					\item \hyperref[href_t:vertical_range_ctl]
%							{\tt vertical\_range\_ctl   [BOTTOM]  [TOP]}
				\end{itemize}
%
    			\item Block \verb|stereo_view_parameter_ctl|
						\label{href_i:stereo_view_parameter_ctl}
				\begin{itemize}
					\item \hyperref[href_t:focal_distance_ctl]
							{\tt focal\_distance\_ctl   [DISTANCE]}
					\item \hyperref[href_t:eye_separation_ctl]
							{\tt eye\_separation\_ctl   [SEPARATION]}
					\item \hyperref[href_t:eye_separation_angle]
							{\tt eye\_separation\_angle   [DEGREE]}
					\item \hyperref[href_t:eye_separation_step_by_angle]
							{\tt eye\_separation\_step\_by\_angle   [ON/OFF]}
				\end{itemize}
%
		\end{itemize}
%
	\item Block \verb|plot_area_ctl|
				\label{href_i:plot_area_ctl}
		\begin{itemize}
			\item \hyperref[href_t:chosen_ele_grp_ctl]
					{\tt chosen\_ele\_grp\_ctl    [AREA\_NAME]}
			\item \hyperref[href_t:surface_enhanse_ctl]
					{\tt surface\_enhanse\_ctl    [SURFACE\_NAME]  [TYPE]  [OPACITY]}
		\end{itemize}
%
	\item File or Block \verb|pvr_color_ctl|
			\label{href_i:pvr_color_ctl}
		\begin{itemize}
    			\item Block \verb|colormap_ctl|
 			\item Block \verb|colorbar_ctl|
		\end{itemize}
%
	\item Block \verb|colormap_ctl|
			\label{href_i:colormap_ctl}
		\begin{itemize}
			\item \hyperref[href_t:colormap_mode_ctl]
					{\tt colormap\_mode\_ctl    [MODE]}
			\item \hyperref[href_t:background_color_ctl]
					{\tt background\_color\_ctl    [MODE]}
%
%			\item \hyperref[href_t:LIC_color_field]
%					{\tt LIC\_color\_field    [Field\_Name]}
%			\item \hyperref[href_t:LIC_color_componenet]
%					{\tt LIC\_color\_componenet    [Component\_Name]}
%			\item \hyperref[href_t:LIC_transparent_field]
%					{\tt LIC\_transparent\_field    [Field\_Name]}
%			\item \hyperref[href_t:LIC_transparent_componenet]
%					{\tt LIC\_transparent\_componenet    [Component\_Name]}
%
			\item \hyperref[href_t:data_mapping_ctl]
					{\tt data\_mapping\_ctl    [TYPE]}
			\item \hyperref[href_t:range_min_ctl]
					{\tt range\_min\_ctl    []MIN\_VALUE}
			\item \hyperref[href_t:range_max_ctl]
					{\tt range\_max\_ctl    [MAX\_VALUE]}
			\item \hyperref[href_t:color_table_ctl]
					Array {\tt color\_table\_ctl    [VALUE]  [COLOR\_VAL]}
			\item \hyperref[href_t:opacity_style_ctl]
					{\tt opacity\_style\_ctl    [TYPE]}
			\item \hyperref[href_t:constant_opacity_ctl]
					{\tt constant\_opacity\_ctl    [OPACITY]}
			\item \hyperref[href_t:linear_opacity_ctl]
					Array {\tt linear\_opacity\_ctl    [VALUE]  [OPACITY]}
		\end{itemize}
%
	\item Block \verb|colorbar_ctl|
			\label{href_i:colorbar_ctl}
		\begin{itemize}
			\item \hyperref[href_t:colorbar_switch_ctl]
					{\tt colorbar\_switch\_ctl    [ON/OFF]}
			\item \hyperref[href_t:colorbar_scale_ctl]
					{\tt colorbar\_scale\_ctl    [ON/OFF]}
			\item \hyperref[href_t:font_size_ctl]
					{\tt font\_size\_ctl    [SIZE]}
			\item \hyperref[href_t:num_grid_ctl]
					{\tt num\_grid\_ctl    [\# of grid]}
			\item \hyperref[href_t:zeromarker_switch]
					{\tt zeromarker\_switch    [ON/OFF]}
			\item \hyperref[href_t:colorbar_range]
					{\tt colorbar\_range    [MIN]  [MAX]}
			\item \hyperref[href_t:axis_label_switch]
					{\tt axis\_label\_switch    [ON/OFF]}
			\item \hyperref[href_t:time_label_switch]
					{\tt time\_label\_switch    [ON/OFF]}
			\item \hyperref[href_t:map_grid_switch]
					{\tt map\_grid\_switch    [ON/OFF]}
		\end{itemize}
%
	\item File or Block \verb|lighting_ctl  [File_Name]|
				\label{href_i:lighting_ctl}
		\begin{itemize}
			\item \hyperref[href_t:ambient_coef_ctl]
					{\tt ambient\_coef\_ctl     [VALUE]}
			\item \hyperref[href_t:diffuse_coef_ctl]
					{\tt diffuse\_coef\_ctl     [VALUE]}
			\item \hyperref[href_t:specular_coef_ctl]
					{\tt specular\_coef\_ctl     [VALUE]}
			\item \hyperref[href_t:position_of_lights]
					Array {\tt position\_of\_lights     [X]  [Y]  [Z]}
			\item \hyperref[href_t:sph_position_of_lights]
					Array {\tt sph\_position\_of\_lights     [R]  [THETA]  [PHI]}
		\end{itemize}
%
	\item Array Block \verb|section_ctl|
				\label{href_i:section_ctl}
		\begin{itemize}
   			 \item File or Block \hyperref[href_t:surface_define]
			 		{\tt surface\_define  [File\_Name]}
			\item \hyperref[href_t:opacity_ctl]
					{\tt opacity\_ctl     [VALUE]}
			\item \hyperref[href_t:zeroline_switch_ctl]
				{\tt zeroline\_switch\_ctl     [ON/OFF]}
		\end{itemize}
%
	\item Array Block \verb|isosurface_ctl|
				\label{href_i:isosurface_ctl}
		\begin{itemize}
			\item \hyperref[href_t:isosurf_value]
					{\tt isosurf\_value     [VALUE]}
			\item \hyperref[href_t:opacity_ctl]
					{\tt opacity\_ctl     [VALUE]}
			\item \hyperref[href_t:surface_direction]
					{\tt surface\_direction     [DIRECTION]}
		\end{itemize}
%
	\item Block        \verb|quilt_image_ctl|
			\label{href_i:quilt_image_ctl}
		\begin{itemize}
			\item \hyperref[href_t:num_column_row_ctl]
					{\tt num\_column\_row\_ctl     [\# of column] [\# of row]}
			\item \hyperref[href_t:num_row_column_ctl]
					{\tt num\_row\_column\_ctl     [\# of row] [\# of column]}
	    	\item Array Block \verb|view_transform_ctl|
					\label{href_i:quilt_view_transform_ctl}
		\end{itemize}
%
	\item Block        \verb|snapshot_movie_ctl|
				\label{href_i:snapshot_movie_ctl}
		\begin{itemize}
			\item \hyperref[href_t:movie_mode_ctl]
					{\tt movie\_mode\_ctl       [Mode]}
			\item \hyperref[href_t:num_frames_ctl]
					{\tt num\_frames\_ctl       [\# of Flame]}
			\item \hyperref[href_t:rotation_axis_ctl]
					{\tt rotation\_axis\_ctl    [X/Y/Z]}
			\item \hyperref[href_t:angle_range]
					{\tt angle\_range    [START] [END]}
			\item \hyperref[href_t:apature_range]
					{\tt apature\_range  [START] [END]}
			\item \hyperref[href_t:LIC_kernel_peak_range]
					{\tt LIC\_kernel\_peak\_range  [START] [END]}
%
	    		\item File or Block \verb|start_view_control [File_Name]|
					\label{href_i:start_view_control}
	   	 	\item File or Block \verb|end_view_control  [File_Name]|
					\label{href_i:end_view_control}
	  	  	\item Array File or Block \verb|view_transform_ctl  [File_Name] |
					\label{href_i:movie_view_transform_ctl}
		\end{itemize}
\end{itemize}


\subsection{Map projection data (Parallel volume rendering module)}
Map projection module generate visualization image using map projection through surfacing module. Currently, contour plots for scalar fields can only be generated, and Aitoff projection is only supported in this module.

To output map projection data, increment of the map projection needs to be defined at \verb|i_step_map_projection_ctl| in \verb|time_step_ctl| block. Parameters foe each rendering are defined in array block \verb|map_rendering_ctl| in \verb|visual_control|. Same the other visualizatiom modules, each  \verb|map_rendering_ctl| block can be stored in an external file, and the external file can be defined as \\
 \verb|file map_rendering_ctl [File_Name]|.
%
\paragraph{Control data}
The control parameters for map projection module is the following:
\\
%
Block \verb|map_rendering_ctl| (Top level for map prodection)
\\
\label{href_i:map_rendering_ctl}
\begin{itemize}
	\item \hyperref[href_t:map_image_prefix]
			{\tt map\_image\_prefix    [File\_Prefix]}
	\item \hyperref[href_t:map_image_format]
			{\tt map\_image\_format    [File\_Format]}
%
	\item \hyperref[href_t:output_field]
			{\tt output\_field            [Field\_Name]}
	\item \hyperref[href_t:output_component]
			{\tt output\_component       [Component\_Name]}
	\item \hyperref[href_t:isoline_field]
			{\tt isoline\_field                [Field\_Name]}
	\item \hyperref[href_t:isoline_component]
			{\tt isoline\_component     [Component\_Name]}
%
	\item Block \verb|section_ctl|
			\label{href_i:map_section_ctl}
		\begin{itemize}
    			\item File or Block \verb|surface_define|
						\label{href_i:map_surface_define}
%
			\item \hyperref[href_t:zeroline_switch_ctl]
					{\tt zeroline\_switch\_ctl     [ON/OFF]}
			\item \hyperref[href_t:isoline_color_mode]
					{\tt isoline\_color\_mode     [MODE]}
			\item \hyperref[href_t:isoline_number_ctl]
					{\tt isoline\_number\_ctl     [\# of LINES]}
			\item \hyperref[href_t:isoline_range_ctl]
					{\tt isoline\_range\_ctl     [MIN\_VALUE]  [MAX\_VALUE]}
			\item \hyperref[href_t:isoline_width_ctl]
					{\tt isoline\_width\_ctl     [WIDTH]}
			\item \hyperref[href_t:grid_width_ctl]
					{\tt grid\_width\_ctl     [WIDTH]}
			\item \hyperref[href_t:tangent_cylinder_switch_ctl]
					{\tt tangent\_cylinder\_switch\_ctl     [ON/OFF]}
			\item \hyperref[href_t:inner_radius_ctl]
					{\tt inner\_radius\_ctl     [RADIUS]}
			\item \hyperref[href_t:outer_radius_ctl]
					{\tt outer\_radius\_ctl     [RADIUS]}
		\end{itemize}
%
	\item File or Block \verb|map_projection_ctl|
				\label{href_i:map_projection_ctl}
		\begin{itemize}
    			\item Block \verb|image_size_ctl|
						\label{href_i:image_size_ctl}
				\begin{itemize}
					\item \hyperref[href_t:x_pixel_ctl]
							{\tt x\_pixel\_ctl   [\# of PIXELS]}
					\item \hyperref[href_t:y_pixel_ctl]
							{\tt y\_pixel\_ctl   [\# of PIXELS]}
				\end{itemize}
%
%			\item Array \hyperref[href_t:modelview_matrix_ctl]
%					{\tt modelview\_matrix\_ctl   [X/Y/X/W] [X/Y/Z/W]  [VALUE]}
%			\item Array \hyperref[href_t:look_at_point_ctl]
%					{\tt look\_at\_point\_ctl   [X/Y/Z]    [VALUE]}
%			\item Array \hyperref[href_t:eye_position_ctl]
%					{\tt eye\_position\_ctl   [X/Y/Z]     [VALUE]}
%			\item Array \hyperref[href_t:up_direction_ctl]
%					{\tt up\_direction\_ctl   [X/Y/Z]     [VALUE]}
%			\item Array \hyperref[href_t:view_rotation_vec_ctl]
%					{\tt view\_rotation\_vec\_ctl   [X/Y/Z]     [VALUE]}
%			\item \hyperref[href_t:view_rotation_deg_ctl]
%					{\tt view\_rotation\_deg\_ctl     [DEGREE]}
%			\item \hyperref[href_t:scale_factor_ctl]
%					{\tt scale\_factor\_ctl     [SCALE]}
%			\item Array \hyperref[href_t:scale_factor_vec_ctl]
%					{\tt scale\_factor\_vec\_ctl  [X/Y/Z]     [SCALE]}
%			\item Array \hyperref[href_t:eye_position_in_viewer_ctl]
%					{\tt eye\_position\_in\_viewer\_ctl   [X/Y/Z]    [VALUE]}
%
			\item \hyperref[href_t:projection_type_ctl]
					{\tt projection\_type\_ctl   [TYPE]}
%
   			\item Block \verb|projection_matrix_ctl|
						\label{href_i:projection_matrix_ctl}
				\begin{itemize}
%					\item \hyperref[href_t:perspective_angle_ctl]
%							{\tt perspective\_angle\_ctl   [DEGREE]}
%					\item \hyperref[href_t:perspective_xy_ratio_ctl]
%							{\tt perspective\_xy\_ratio\_ctl   [ASPECT]}
%					\item \hyperref[href_t:perspective_near_ctl]
%							{\tt perspective\_near\_ctl   [NEAR\_DISTANCE]}
%					\item \hyperref[href_t:perspective_far_ctl]
%							{\tt perspective\_far\_ctl   [FAR\_DISTANCE]}
%
					\item \hyperref[href_t:horizontal_range_ctl]
							{\tt horizontal\_range\_ctl   [LEFT]  [RIGHT[}
					\item \hyperref[href_t:vertical_range_ctl]
							{\tt vertical\_range\_ctl   [BOTTOM]  [TOP]}
				\end{itemize}
		\end{itemize}
%
	\item File \verb|map_color_ctl|
				\label{href_i:map_color_ctl}
		\begin{itemize}
    			\item Block \verb|colormap_ctl|
 			\item Block \verb|colorbar_ctl|
		\end{itemize}
%
	\item Block \verb|colormap_ctl|
				\label{href_i:colormap_ctl}
		\begin{itemize}
			\item \hyperref[href_t:colormap_mode_ctl]
					{\tt colormap\_mode\_ctl    [MODE]}
			\item \hyperref[href_t:background_color_ctl]
					{\tt background\_color\_ctl    [MODE]}
%
			\item \hyperref[href_t:data_mapping_ctl]
					{\tt data\_mapping\_ctl    [TYPE]}
			\item \hyperref[href_t:range_min_ctl]
					{\tt range\_min\_ctl    []MIN\_VALUE}
			\item \hyperref[href_t:range_max_ctl]
					{\tt range\_max\_ctl    [MAX\_VALUE]}
			\item \hyperref[href_t:color_table_ctl]
					Array {\tt color\_table\_ctl    [VALUE]  [COLOR\_VAL]}
		\end{itemize}
%
	\item Block \verb|colorbar_ctl|
			\label{href_i:colorbar_ctl}
		\begin{itemize}
			\item \hyperref[href_t:colorbar_switch_ctl]
					{\tt colorbar\_switch\_ctl    [ON/OFF]}
			\item \hyperref[href_t:colorbar_scale_ctl]
					{\tt colorbar\_scale\_ctl    [ON/OFF]}
			\item \hyperref[href_t:font_size_ctl]
					{\tt font\_size\_ctl    [SIZE]}
			\item \hyperref[href_t:num_grid_ctl]
					{\tt num\_grid\_ctl    [\# of grid]}
			\item \hyperref[href_t:zeromarker_switch]
					{\tt zeromarker\_switch    [ON/OFF]}
			\item \hyperref[href_t:colorbar_range]
					{\tt colorbar\_range    [MIN]  [MAX]}
			\item \hyperref[href_t:time_label_switch]
					{\tt time\_label\_switch    [ON/OFF]}
			\item \hyperref[href_t:map_grid_switch]
					{\tt map\_grid\_switch    [ON/OFF]}
		\end{itemize}
\end{itemize}



\subsubsection{\tt volume\_rendering}
\label{href_t:volume_rendering}
%
\paragraph{\tt updated\_sign}
\label{href_t:updated_sign}  
\verb|[SIGNAL]| \\
The program will read again PVR parameter files and updates PVR parameters if the text \verb|[SIGNAL]| is changed. 
%
\paragraph{\tt pvr\_file\_prefix}
\label{href_t:pvr_file_prefix}  
\verb|[File_Prefix]| \\
File prefix of the output image file  \verb|[File_Prefix]| is defined by text. 
%
\paragraph{\tt pvr\_output\_format}
\label{href_t:pvr_output_format}  
\verb|[File_Format]| \\
File format of the output image file  \verb|[File_Format]| is defined by text.  The following format can be defined.
\begin{description}
\item{\tt BMP: }               Bitmap format
\item{\tt PNG: }               PNG format  (zlib or libpng is required to build)
\item{\tt QUILT: }             BMP Quilt format for holograms
\item{\tt QUILT\_GZ: }      Compressed BMP Quilt format for holograms
\end{description}
%
\paragraph{\tt monitoring\_mode}
\label{href_t:monitoring_mode}  
\verb|[ON/OFF]| \\
When the monitoring mode is turned on, the program outputs two same image files. One file is named with step number, and another file is named without step number. Consequently, the image file without step number is overwritten every PVR data output. During the simulation, we can check the latest image.
%
\paragraph{\tt stereo\_imaging}
\label{href_t:stereo_imaging}  
\verb|[ON/OFF]| \\
When stereo imaging switch is turned on, Stereo image is generated. In stereo imaing mode, the following \hyperref[href_t:anaglyph_switch]{\tt anaglyph\_switch} or \hyperref[href_t:quilt_3d_imaging]{\tt quilt\_3d\_imaging} needs to be turned on.
%
\paragraph{\tt anaglyph\_switch}
\label{href_t:anaglyph_switch}  
\verb|[ON/OFF]| \\
When anaglyph switch is turned on, stereo anaglyph image is generated. To look anaglyph, red and blue glass is required.
%
\paragraph{\tt quilt\_3d\_imaging}
\label{href_t:quilt_3d_imaging}  
\verb|[ON/OFF]| \\
When anaglyph switch is turned on, stereo image for looking glass is generated. This switch is also turned on if stereo image with side-by-side is generated.
%
\paragraph{\tt output\_field}
\label{href_t:output_field}  
\verb|[Field_Name]| \\
Field name \verb|[Field_Name]| for rendering is defined by text.
%
\paragraph{\tt output\_component}
\label{href_t:output_component}  
\verb|[Component_Name]| \\
Component name \verb|[Component_Name]| for rendering is defined by text.
%
\subsubsection{\tt view\_transform\_ctl}
\label{href_t:view_transform_ctl}
Parameters for view point and direction are defined in this block. This block can be saved into an external file. (Go to \hyperref[href_i:view_transform_ctl] {\tt view\_transform\_ctl})

\subsubsection*{\tt image\_size\_ctl}
\label{href_t:image_size_ctl}
Image size (number of pixels) are defined in this block. (Go to \hyperref[href_i:image_size_ctl] {\tt image\_size\_ctl})
%
\paragraph{\tt x\_pixel\_ctl}
\label{href_t:x_pixel_ctl}  
\verb|[\# of PIXELS]| \\
Number of pixels in the horizontal direction \verb|[\# of PIXELS]| is defined by integer.
%
\paragraph{\tt y\_pixel\_ctl}
\label{href_t:y_pixel_ctl}  
\verb|[\# of PIXELS]| \\
Number of pixels in the vertical direction \verb|[\# of PIXELS]| is defined by integer.
%
\paragraph{\tt modelview\_matrix\_ctl}
\label{href_t:modelview_matrix_ctl}  
\verb|[X/Y/X/W] [X/Y/Z/W]  [VALUE]| \\
Modelview matrix $A_{ij}$ is defined by array. Directions of row and columns are defined in the first and second texts, respectively, and the value of the each matrix component is defined by the third real value.
%
\paragraph{\tt look\_at\_point\_ctl}
\label{href_t:look_at_point_ctl}  
\verb|[X/Y/X] [VALUE]| \\
Position to look at is defined by array. Directions are defined in the first text, and the value is defined by the third real value.
%
\paragraph{\tt eye\_position\_ctl}
\label{href_t:eye_position_ctl}  
\verb|[X/Y/X] [VALUE]| \\
Position of eye (or camera) is defined by array. Directions are defined in the first text, and the value is defined by the third real value.
%
%

%
\subsubsection{\tt map\_rendering\_ctl}
\label{href_t:map_rendering_ctl}
%


